HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-07-15 scnn.tex
architecture subsection

\todo{Should we give a more general / high-level description of a CNN?}

A CNN is composed of the following main building blocks~\citep{lecun1998cnn}, illustrated in~\figref{architecture}: (i) a convolution, (ii) a non-linearity, (iii) a down-sampling operation, (iv) a pooling operation, and (v), optionally, some normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training. We verified this experimentally in our setting as well.} As operations (ii) and (v) are point-wise, they do not depend on the data domain. The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either. The convolution and down-sampling operations however need to be generalized from Euclidean domains to the sphere.

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width=0.45\textwidth]{figures/pooling.pdf}
	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarsest cell covers $1/12$ of the sphere.}
	\label{fig:pooling}
\end{figure}

\section{Experiments}
\label{sec:experiments}
\assign{Nathanaël, Tomek}

@@

\begin{figure*}[!ht]
\centering
\includegraphics[width=0.48\textwidth]{figures/smooth_map_class_1.pdf}
\includegraphics[width=0.48\textwidth]{figures/smooth_map_class_2.pdf}
\caption{Example maps from two classes. Top: model 1 ($\Omega_m=0.31, \sigma_8=0.82$). Bottom: model 2 ($\Omega_m=0.26, \sigma_8=0.91$).
The initial conditions for these simulations were the same, so differences arise only due to different cosmological parameters. \nati{Tomek: Is this correct?}}
\label{fig:map_sample}
\end{figure*}

>>>>

A CNN is composed of the following main building blocks~\citep{lecun1998cnn}: (i) a convolution, (ii) a non-linearity, (iii) a down-sampling operation, (iv) a pooling operation, and (v), optionally, some normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training. We verified this experimentally in our setting as well.} Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}. As operations (ii) and (v) are point-wise, they do not depend on the data domain. The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either. The convolution and down-sampling operations however need to be generalized from Euclidean domains to the sphere.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{figures/pooling.pdf}
	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarsest cell covers $1/12$ of the sphere.}
	\label{fig:pooling}
\end{figure}

\subsection{Architecture}
\label{sec:architecture}

Now that all the building blocks are defined, let's discuss our proposed spherical CNN architecture, pictured in \figref{architecture}.

\todo{present and discuss the whole CNN architecture.}

Learning the $\theta_k$.

\section{Experiments}
\label{sec:experiments}

@@

\begin{figure*}[!ht]
\centering
\includegraphics[width=0.48\textwidth]{figures/smooth_map_class_1.pdf}
\includegraphics[width=0.48\textwidth]{figures/smooth_map_class_2.pdf}
\caption{Example maps from two classes to be discriminated. Left: model 1 with $\Omega_m=0.31$ and $\sigma_8=0.82$. Right: model 2 with $\Omega_m=0.26$ and $\sigma_8=0.91$.
The initial conditions for both simulations were the same, so differences only arise due to different cosmological parameters. \nati{Tomek: Is this correct?}}
\label{fig:map_sample}
\end{figure*}
